A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-07-23 paper.tex
typo
ENH: ready for first arXiv upload

\subsection{Nash-equilibrium concepts and statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
%% = q_0$ by definition of $e_1$ and
%% $e_2$. 
At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\tilde{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{eqnarray}
  \begin{split}
  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}

@@

\paragraph{Our contribution.}
Developing on an alternative notion of approximate equilibria
homologuous to that presented in Definition \ref{thm:approx_nash}, we
device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
computing approximate Nash equilibria in sequential two-person
zero-sum games with imcomplete information and perfect recall. We also
prove that the number of iterations required by the algorithm to
produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$.

@@

@@

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item[--] avoid having to compute the projections $\proj_{Q_k}$,
\item[--] have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps.
\end{itemize}

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\section{A more amenable notion of approximate equilibrium}
\subsection{Interlude: Proximal calculus}
Let us introduce some notions in modern convex analysis which will be
useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
y^*, x^*, q^*)$.
\label{thm:cool_notion}
\end{definition}

@@

\section{The proposed primal-dual algorithm}
\label{sec:algo}
We now derive and establish the theoretical properties of the
algorithm which is the main object of this manuscript.

\subsection{Algorithm and convergence rate}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\epsilon,0)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.

%% \begin{definition}(Kronecker product)
%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by

%% \begin{equation}
%% F \otimes B:=\left[
%% \begin{array}{cccc}
%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
%% \vdots & \vdots & \ddots & \vdots\\
%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
%% \end{equation}
%% \end{definition}

%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
%% easily verfies that $Y$ is the matrix product of the ``small''
%% matrices $B$, $X$, and $F^T$, i.e

%% \begin{equation}
%%   \label{eq:kron_matvec}
%%   Y = BXF^T
%% \end{equation}

%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
%% written as block-diagonal matrix whose blocks are sums of Kronecker
%% products of much smaller sparse matrices as follows

%% \begin{equation}
%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
%% \label{eq:factor_A}
%% \end{equation}
%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
%% sequences of moves in round $i$ which end in a \textit{fold} action,
%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
%% encodes the betting structure of round $i$, while $W$ encodes the
%% wind/lose/draw information determined by ranking the players' hands at
%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
%% enough to be explictly represented whereas it is infeasible to
%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
%% $S$, and $W$ are themselves sparse, which allows one to use the
%% compressed row storage data structure that only stores nonzero entries
%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
%% programming language).

%% Such a representation of the payoff matrix $A$ trivializes matvec
%% operations involving $A$ or $A^T$ (thanks to formula
%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
%% exploiting the sparsity of these blocks themselves). Of course, one
%% can always write the payoff matrix $A$ of a flop-type Poker game in a
%% form similary to \eqref{eq:factor_A} by applying appropriate
%% permutations to the enumeration of the players's sequences.

\paragraph{\textbf{Computing $\|K\|$.}} Power iteration (Perron-Frobenius)...

\section{Experimental results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
experimented it on real games.

\subsection{Basic test-bed: Matrix games on simplexes}
As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
\times 1000$ random matrix whose entries are uniformly identically
distributed in the closed interval $[-1, 1]$.

\begin{figure}[!htpb]
  \subfigure[Matrix game on simplexes]{
    \includegraphics[width=.33\linewidth]{0.pdf}
  }
  \hspace{-2em}
  \subfigure[Toy Poker]{
    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
  }
  \hspace{-2em}
  \subfigure[Kuhn 3-card Poker]{
    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-1em}
  \includegraphics[width=.34\linewidth]{1.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
    primal-dual gap. \textbf{Bottom row}: Evolution of
    value of game.}
  \label{Tab:dgap_curve}
\end{figure}

\subsection{Sequential games with imcomplete information}
\paragraph{\textbf{Toy Poker game...}}
%% The sequence-form representation for this Toy Poker game is given by
%% (showing only nonzero entries):\\

>>>>

\subsection{Nash-equilibrium concepts and statement of the problem}
The sequence-form representation for two-person zero-sum games with
imcomplete information was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for such games, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP (Linear Convex Program)
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
%% = q_0$ by definition of $e_1$ and
%% $e_2$. 
At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\tilde{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{eqnarray}
  \begin{split}
  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (-\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}

@@

@@

\subsection{Our contribution}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear indication whatsoever,
on whether progress is being made or not. So need to way to
\begin{itemize}
\item[--] avoid having to compute the projections $\proj_{Q_k}$,
\item[--] have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps.
\end{itemize}

Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologuous to that presented in Definition \ref{thm:approx_nash}, we
device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
computing approximate Nash equilibria in sequential two-person
zero-sum games with imcomplete information and perfect recall. We also
prove (Theorem \ref{thm:pd})
that the number of iterations required by the algorithm to
produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$.%%  The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.

@@

\section{Our contributions}
\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\subsection{A more amenable notion of approximate equilibria}
\subsubsection{Interlude: Proximal calculus}
Let us introduce some notions from modern convex analysis which will be
useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

Such a vector $v^*$ is called a Nash $(\epsilon_1, \epsilon_2)$-residual at $(x^*,
y^*, x^*, q^*)$.
\label{thm:cool_notion}
\end{definition}

@@

\subsection{The proposed primal-dual algorithm}
\label{sec:algo}
We now derive and establish the theoretical properties of the
algorithm which is the main object of this manuscript.

\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\epsilon,0)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}. For the purpose of
completeness, we explain the details of the tricks used in
\cite{hoda2010smoothing} for speeding up the computation of these
matvec products.

\begin{definition}(Kronecker product)
Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
  s}$ be matrices. The kronecker product of $F$ and $B$ is defined by

\begin{equation}
F \otimes B:=\left[
\begin{array}{cccc}
F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
\vdots & \vdots & \ddots & \vdots\\
F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
\end{array}\right] \in \mathbb{R}^{mr \times ns}
\end{equation}
\end{definition}

One notes that $(F \otimes B)^T = F^T \otimes B^T$.
$F \otimes B$ can be very much larger than both $F$ and $B$ in
dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
easily verfies that $Y$ is the matrix product of the ``small''
matrices $B$, $X$, and $F^T$, i.e

\begin{equation}
  \label{eq:kron_matvec}
  Y = BXF^T
\end{equation}

Now, in Texas Hold'em for example, the payoff matrix $A$ can be
written as block-diagonal matrix whose blocks are sums of Kronecker
products of much smaller sparse matrices as follows

\begin{equation}
  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
    \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
    B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
\label{eq:factor_A}
\end{equation}
See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
sequences of moves in round $i$ which end in a \textit{fold} action,
and $S$ to the sequences which end in a \textit{showdown}. $B_i$
encodes the betting structure of round $i$, while $W$ encodes the
wind/lose/draw information determined by ranking the players' hands at
showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
enough to be explictly represented whereas it is infeasible to
explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
$S$, and $W$ are themselves sparse, which allows one to use the
compressed row storage data structure that only stores nonzero entries
(for example \textit{scipy.sparse.csr\_matrix}, in the Python
programming language).

Such a representation of the payoff matrix $A$ trivializes matvec
operations involving $A$ or $A^T$ (thanks to formula
\eqref{eq:kron_matvec} above, applied to their diagonal blocks and
exploiting the sparsity of these blocks themselves). Of course, one
can always write the payoff matrix $A$ of a flop-type Poker game in a
form similary to \eqref{eq:factor_A} by applying appropriate
permutations to the enumeration of the players's sequences.

\paragraph{\textbf{Computing $\|K\|$.}}
Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
computed using the power iteration (Perron-Frobenius).

\section{Experimental results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
tested it on simulated and real games.
\paragraph{Basic test-bed: Matrix games on simplexes.}
As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
\times 1000$ random matrix whose entries are uniformly identically
distributed in the closed interval $[-1, 1]$. We compared our proposed
Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and Gilpin's et
al. \cite{gilpinfirst}. The results of the benchmarks are shown in
Figure \ref{Tab:dgap_curve}\textit{(a)}...

\begin{figure}[!htpb]
  \subfigure[Matrix game on simplexes]{
    \includegraphics[width=.5\linewidth]{0.pdf}
  }
  %% \hspace{-2em}
  %% \subfigure[Toy Poker]{
  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
  %% }
  \hspace{-2em}
  \subfigure[Kuhn 3-card Poker]{
    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-2em}
  \includegraphics[width=.5\linewidth]{1.pdf}
  %% \hspace{-1em}
  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  \hspace{-1em}
  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
    primal-dual gap. \textbf{Bottom row}: Evolution of
    value of game.}
  \label{Tab:dgap_curve}
\end{figure}

\paragraph{Experiments on sequential games with imcomplete information: Kuhn 3-card
  poker.} This game is a simplified form of poker
developed by Harold W. Kuhn. It is a two-person zero-sum game which is
simply enough to serve as an example but contains all the complexity
traits of a imcomplete information sequential game. The
deck includes only three playing cards, for example a King, Queen, and
Jack. One card is dealt to each player, then the first player must bet
or pass, then the second player may bet or pass. If any player chooses
to bet the opposing player must bet as well ("call") in order to stay
in the round. After both players pass or bet the player with the
highest card wins the pot. The
sequence-form representation of the game has $n_1 = n_2 = 13$
sequences and $l_1 = l_2 = 7$ information
sets per player. The pair $(x^*, y^*) \in \mathbb{R}^{13} \times
\mathbb{R}^{13}$ of realization plans given by
\begin{eqnarray*}
  \begin{split}
    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
      0.275, 0.725]^T,\\
    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
    \end{split}
\end{eqnarray*}
is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
Algorithm  \ref{Tab:algo}. The convergence curves are shown
in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
feasible. Indeed, $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
      \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5},
      -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$
and
$E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
  \times 10^{-6}, -1.50 \times 10^{-6},
      2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
      10^{-7}]^T$.
Finally, one checks that ${x^*}^TAy^* = {-0.05555}$,
 which agrees to 5 d.p with the value of $-1 / 18$ computed
 analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
 evolution of the dual gap and the expected value of the game across
 iterations are shown in Figure \ref{Tab:dgap_curve}.
More details (payoff matrix, etc.) are provided in
the supplementary materials...

\section{Concluding remarks}
Making use of the sequence-form representation
\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
deviced a simple and efficient primal-dual algorithm for computing
Nash equilibria in two-person zero-sum sequential games with
imcomplete information (like Texas Hold'em, etc.). Our algorithm is
simple to implement, with a very low constant cost per iteration, and
enjoys a rigorous convergence theory with a proven
$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
(matvec products, clipping, etc.), to a Nash
$(\epsilon,0)$-equilibrium of the game. Equilibrium problems are
saddle-point convex-concave problems, and as
such a natural choice for algorithms for solving them would be in the
family of primal-dual algorithms. We believe such primal-dual
schemes will receive more attention in the algorithmic game theory
community in future.

The author's implementation of the proposed algorithm is available
upon request.
